maze-dataset

### 2025-03-29 docs/paper/paper.tex
wip

\documentclass[10pt,a4paper,onecolumn]{article}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage[rgb,svgnames]{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{tikz}
\usepackage[pdfa]{hyperref}
\usepackage{hyperxmp}
\hypersetup{%
    unicode=true,
    pdfapart=3,
    pdfaconformance=B,
    pdftitle={A Configurable Library for Generating and Manipulating
Maze Datasets},
    pdfauthor={Michael Igorevich Ivanitskiy, Aaron Sandoval, Alex F.
Spies, Rusheb Shah, Brandon Knutson, , Cecilia Diniz Behn, Samy Wu
Fung},
    pdfpublication={Journal of Open Source Software},
    pdfpublisher={Open Journals},
    pdfissn={2475-9066},
    pdfpubtype={journal},
    pdfvolumenum={},
    pdfissuenum={},
    pdfdoi={N/A},
    pdfcopyright={Copyright (c) 1970, Michael Igorevich Ivanitskiy,
Aaron Sandoval, Alex F. Spies, Rusheb Shah, Brandon Knutson, , Cecilia
Diniz Behn, Samy Wu Fung},
    pdflicenseurl={http://creativecommons.org/licenses/by/4.0/},
    colorlinks=true,
    linkcolor=[rgb]{0.0, 0.5, 1.0},
    citecolor=Blue,
    urlcolor=[rgb]{0.0, 0.5, 1.0},
    breaklinks=true
}
% https://tex.stackexchange.com/a/535849
% Create an OutputIntent in order to correctly specify colours
\immediate\pdfobj stream attr{/N 3} file{sRGB.icc}
\pdfcatalog{%
  /OutputIntents [
    <<
      /Type /OutputIntent
      /S /GTS_PDFA1
      /DestOutputProfile \the\pdflastobj\space 0 R
      /OutputConditionIdentifier (sRGB)
      /Info (sRGB)
    >>
  ]
}
\pdfvariable omitcidset=1
\usepackage{caption}
\usepackage{orcidlink}
\usepackage{tcolorbox}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{seqsplit}
\usepackage{xstring}

@@

\fancyfoot[L]{\parbox[t]{0.98\headwidth}{\footnotesize{\sffamily Ivanitskiy
et al. (1970). A Configurable Library for Generating and Manipulating
Maze Datasets. \emph{Journal of Open Source Software},
\emph{¿VOL?}(¿ISSUE?), ¿PAGE? \url{https://doi.org/N/A}}.}}

@@

\title{A Configurable Library for Generating and Manipulating Maze
Datasets}

\author[1%
%
\ensuremath\mathparagraph]{Michael Igorevich Ivanitskiy%
  \,\orcidlink{0000-0002-4213-4993}\,%
}
\author[%
%
]{Aaron Sandoval%
}
\author[2%
%
]{Alex F. Spies%
  \,\orcidlink{0000-0002-8708-1530}\,%
}
\author[%
%
]{Rusheb Shah%
  \,\orcidlink{0009-0008-3058-0217}\,%
}
\author[%
%
]{Brandon Knutson%
}
\author[1%
%
]{%
  \,\orcidlink{0009-0004-8413-0239}\,%
}
\author[1%
%
]{Cecilia Diniz Behn%
}
\author[1%
%
]{Samy Wu Fung%
}

@@

>>>>

\documentclass[10pt,a4paper,onecolumn]{article}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage[rgb,svgnames]{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{tikz}
\usepackage[pdfa]{hyperref}
\usepackage{hyperxmp}
\hypersetup{%
    unicode=true,
    pdfapart=3,
    pdfaconformance=B,
    pdftitle={maze-dataset},
    pdfauthor={Michael Igorevich Ivanitskiy, Aaron Sandoval, Alex F.
Spies, Rusheb Shah, Brandon Knutson, , Cecilia Diniz Behn, Samy Wu
Fung},
    pdfpublication={Journal of Open Source Software},
    pdfpublisher={Open Journals},
    pdfissn={2475-9066},
    pdfpubtype={journal},
    pdfvolumenum={},
    pdfissuenum={},
    pdfdoi={N/A},
    pdfcopyright={Copyright (c) 1970, Michael Igorevich Ivanitskiy,
Aaron Sandoval, Alex F. Spies, Rusheb Shah, Brandon Knutson, , Cecilia
Diniz Behn, Samy Wu Fung},
    pdflicenseurl={http://creativecommons.org/licenses/by/4.0/},
    colorlinks=true,
    linkcolor=[rgb]{0.0, 0.5, 1.0},
    citecolor=Blue,
    urlcolor=[rgb]{0.0, 0.5, 1.0},
    breaklinks=true
}
% https://tex.stackexchange.com/a/535849
% Create an OutputIntent in order to correctly specify colours
\immediate\pdfobj stream attr{/N 3} file{sRGB.icc}
\pdfcatalog{%
  /OutputIntents [
    <<
      /Type /OutputIntent
      /S /GTS_PDFA1
      /DestOutputProfile \the\pdflastobj\space 0 R
      /OutputConditionIdentifier (sRGB)
      /Info (sRGB)
    >>
  ]
}
\pdfvariable omitcidset=1
\usepackage{caption}
\usepackage{orcidlink}
\usepackage{tcolorbox}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{seqsplit}
\usepackage{xstring}

@@

\fancyfoot[L]{\parbox[t]{0.98\headwidth}{\footnotesize{\sffamily Ivanitskiy
et al. (1970). maze-dataset. \emph{Journal of Open Source Software},
\emph{¿VOL?}(¿ISSUE?), ¿PAGE? \url{https://doi.org/N/A}}.}}

@@

\title{maze-dataset}

\author[1%
%
\ensuremath\mathparagraph]{Michael Igorevich Ivanitskiy%
  \,\orcidlink{0000-0002-4213-4993}\,%
}
\author[%
%
]{Aaron Sandoval%
  \,\orcidlink{0009-0002-8380-6140}\,%
}
\author[2%
%
]{Alex F. Spies%
  \,\orcidlink{0000-0002-8708-1530}\,%
}
\author[%
%
]{Rusheb Shah%
  \,\orcidlink{0009-0008-3058-0217}\,%
}
\author[%
%
]{Brandon Knutson%
}
\author[1%
%
]{%
  \,\orcidlink{0009-0004-8413-0239}\,%
}
\author[1%
%
]{Cecilia Diniz Behn%
  \,\orcidlink{0000-0002-8078-5105}\,%
}
\author[1%
%
]{Samy Wu Fung%
  \,\orcidlink{0000-0002-2926-4582}\,%
}

@@

\colorbox[RGB]{ 176,152,232 }{ \texttt{ <ADJLIST\_START> (0,1) <--> (0,2) ; (1,0) <--> (1,1) ; (0,1) <--> (0,0) ; } }
\colorbox[RGB]{ 176,152,232 }{ \texttt{ (4,0) <--> (3,0) ; (0,2) <--> (0,3) ; (0,4) <--> (1,4) ; (2,2) <--> (3,2) ; } }
\colorbox[RGB]{ 176,152,232 }{ \texttt{ (3,4) <--> (2,4) ; (2,0) <--> (3,0) ; (3,4) <--> (4,4) ; (3,2) <--> (3,3) ; } }
\colorbox[RGB]{ 176,152,232 }{ \texttt{ (2,4) <--> (2,3) ; (1,3) <--> (0,3) ; (1,3) <--> (1,4) ; (1,0) <--> (0,0) ; } }
\colorbox[RGB]{ 176,152,232 }{ \texttt{ (2,1) <--> (2,0) ; (4,2) <--> (4,3) ; (3,2) <--> (3,1) ; (1,2) <--> (0,2) ; } }
\colorbox[RGB]{ 176,152,232 }{ \texttt{ (4,1) <--> (4,0) ; (4,2) <--> (4,1) ; (4,3) <--> (4,4) ; (1,2) <--> (2,2) ; } }
\colorbox[RGB]{ 176,152,232 }{ \texttt{ (2,1) <--> (2,2) ; <ADJLIST\_END> } }
\newline
\colorbox[RGB]{ 154,239,123 }{ \texttt{ <ORIGIN\_START> (1,3) <ORIGIN\_END> } }
\colorbox[RGB]{ 246,136,136 }{ \texttt{ <TARGET\_START> (2,3) <TARGET\_END> } }
\colorbox[RGB]{ 111,187,254 }{ \texttt{ <PATH\_START> (1,3) (0,3) (0,2) (1,2) (2,2) (2,1) (2,0) (3,0) (4,0) (4,1) } }
\colorbox[RGB]{ 111,187,254 }{ \texttt{ (4,2) (4,3) (4,4) (3,4) (2,4) (2,3) <PATH\_END> } }
